\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-15 paper.qmd

The value for $b_2$ is computed by fixing $b_1$. Considering the lower bound of the NLDR, $a_1 > -2q$, and $a_1 > \frac{1+q}{b_1 -1}$. Similarly, according to the upper bound of the NLDR, $a_1 > \frac{2r_2(1 + q)}{\sqrt{3}(b_2 - 1)}$, because $a_2 = \frac{\sqrt(3)}{2}a_1$ for regular hexagons. Therefore, $b_2 = \Big\lceil1 +\frac{2r_2(b_1 - 1)}{\sqrt{3}}\Big\rceil$.

>>>>

The value for $b_2$ is computed by fixing $b_1$. Considering the upper bound of the first NLDR component, $a_1 > \frac{1+q}{b_1 -3}$. Similarly, for the second NLDR component, $a_2 > \frac{r_2(1 + q)}{(b_2 - 2)}$. Since $a_2 = \frac{\sqrt(3)}{2}a_1$ for regular hexagons, $a_1 > \frac{2r_2(1 + q)}{\sqrt{3}(b_2 - 2)}$. This is a linear optimization problem. Therefore, the optimal solution must occur on a vertex. Therefore, $b_2 = \Big\lceil2 +\frac{2r_2(b_1 - 3)}{\sqrt{3}}\Big\rceil$.

### 2024-07-15 paper.tex

The value for \(b_2\) is computed by fixing \(b_1\). Considering the
lower bound of the NLDR, \(a_1 > -2q\), and
\(a_1 > \frac{1+q}{b_1 -1}\). Similarly, according to the upper bound of
the NLDR, \(a_1 > \frac{2r_2(1 + q)}{\sqrt{3}(b_2 - 1)}\), because
\(a_2 = \frac{\sqrt(3)}{2}a_1\) for regular hexagons. Therefore,
\(b_2 = \Big\lceil1 +\frac{2r_2(b_1 - 1)}{\sqrt{3}}\Big\rceil\).

>>>>

The value for \(b_2\) is computed by fixing \(b_1\). Considering the
upper bound of the first NLDR component, \(a_1 > \frac{1+q}{b_1 -3}\).
Similarly, for the second NLDR component,
\(a_2 > \frac{r_2(1 + q)}{(b_2 - 2)}\). Since
\(a_2 = \frac{\sqrt(3)}{2}a_1\) for regular hexagons,
\(a_1 > \frac{2r_2(1 + q)}{\sqrt{3}(b_2 - 2)}\). This is a linear
optimization problem. Therefore, the optimal solution must occur on a
vertex. Therefore,
\(b_2 = \Big\lceil2 +\frac{2r_2(b_1 - 3)}{\sqrt{3}}\Big\rceil\).
